% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%


%  Ed added the following packages %%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{url}
%\def\UrlFont{\rmfamily}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
%\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[square,sort,comma,numbers]{natbib}

%\usepackage{fix-cm}
\usepackage{graphicx}  
\usepackage[hidelinks]{hyperref}  % for including hyperlinks in document, the hidelinks removes the green box in the pdf
%\usepackage{listings} % for source code listing
%\usepackage{color} % for source code listing

\usepackage{nccmath}
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
%\usepackage{pifont}% http://ctan.org/pkg/pifont

%\usepackage{microtype} % relaxes the rules for inter word spacing 
%\usepackage[T1]{fontenc}
%\usepackage{lmodern}

\usepackage{tabularray}   % for table 
\usepackage{multirow}     % for centering content in a table 
%\usepackage{array, booktabs, ragged2e}
%\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
%\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

% Change the title of the Bibliography to References and make it left-justified
%\renewcommand{\bibname}{References}
%\makeatletter
%\renewcommand\bibsection{
	%	\section*{\refname\@mkboth{\MakeUppercase{\refname}}{\MakeUppercase{\refname}}}
	%}
%\makeatother

% Change the title of the Bibliography to References
%\def\bibname{References}

\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}

% Ed Stopped adding packages here %%%%%%%%%%%%%%%%%%

\begin{document}
%
\title{Exploring the Efficiency \& Cost-Effectiveness of Distributed Computing for Test Execution}
%
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
\titlerunning{Distributed Computing for Test Execution}
%
%
\author{Mrudini Patel\inst{1} \and
Deshawn Knight\inst{1}}
%
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
\authorrunning{M. Patel, D. Knight}
%
%
\institute{University of Guelph, Guelph ON N1G 2W1, CA}
%
\maketitle              % typeset the header of the contribution
%
%
\begin{abstract}
As modern software systems evolve in complexity, the demand for efficient and rapid software testing becomes increasingly more critical. Distributed computing offers a promising solution to improve software test execution as it enables organizations to deliver high-quality software products at an accelerated rate. This paper examines the extent to which test execution can leverage distributed computing to improve efficiency and speed, while focusing on factors such as memory and CPU usage, execution time, and the trade-offs between vertical and horizontal scaling. By distributing tests across multiple machines, memory and CPU loads can be better balanced, potentially reducing the bottlenecks that often delay testing on single-machine environments. Distributed testing introduces concerns of scalability and cost-effectiveness, as larger infrastructures may increase overhead and require additional resources.  Horizontal scaling can parallelize testing processes across multiple machines, promising faster test execution but often at a higher cost. Whereas vertical scaling may limit costs but fail to achieve the same efficient performance. As a result, this paper aims to compare the benefits and limitations of vertical and horizontal scaling in distributed environments, analyzing which approach is more efficient under certain conditions. 

\keywords{Automated Testing  \and Distributed Computing.}
\end{abstract}
%
%
\input{Introduction}
\input{Background}
\input{Methodology}
\input{Findings}
\input{Discussion}
\input{Conclusion}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{plain} % or another style you're using
\bibliographystyle{splncs04}
\bibliography{bibliography}

% \input{Appendix}

\end{document}
